Learning Excursion Sets of Vector-valued Gaussian Random Fields for Autonomous Ocean Sampling

### 2020-07-01 cover_letter/cover_letter.tex
Updates from Overleaf

We thank the editors and reviewers for providing feedback on our manuscript \textbf{AOAS1910-027}. The feedback have been insightful and constructive. Inspired by comments by the referees regarding the scope of the paper, we have spent substantial energy polishing its statistical character and also made an effort keeping the oceanograhic detail compact, yet sufficiently informative for the paper to be readable also by more application-driven research communities (in maritime sciences but also for instance in robotics and AI). From the statistical and mathematical side, we have tried our best to revise the formalism in such a way that further contributions can be built on top of ours, and also that we valorize some secondary findings that we have made along the way and that could be useful to researchers and practitioners from spatial statistics and beyond. This include a very modular (and conceptually appealing) way to present batch-sequential co-Kriging update formulae in heterotopic settings, generalities about excursion measures/volumes of (measurable) random fields, and also technical results towards the calculation of Stepwise Uncertainty Reduction in the vector-valued case. In particular, generalizing our former results enabled use to tackle in the revised version an arbitrary number of responses, as well as to calculate the expected excursion measure variance (on top of the expected integrated Bernoulli variance).\\

>>>>

We thank the editors and reviewers for providing feedback on our manuscript \textbf{AOAS1910-027}. The feedback have been insightful and constructive. Inspired by comments by the referees regarding the scope of the paper, we have spent substantial energy polishing its statistical character and also made an effort keeping the oceanographic detail compact, yet sufficiently informative for the paper to be readable also by more application-driven research communities (in maritime sciences but also for instance in robotics and AI). From the statistical and mathematical side, we have tried our best to revise the formalism in such a way that further contributions can be built on top of ours, and also that we valorize some secondary findings that we have made along the way and that could be useful to researchers and practitioners from spatial statistics and beyond. This include a very modular (and conceptually appealing) way to present batch-sequential co-Kriging update formulae in heterotopic settings, generalities about excursion measures/volumes of (measurable) random fields, and also technical results towards the calculation of Stepwise Uncertainty Reduction in the vector-valued case. In particular, generalizing our former results enabled use to tackle in the revised version an arbitrary number of responses, as well as to calculate the expected excursion measure variance (on top of the expected integrated Bernoulli variance).\\
